### 2016-07-07 image_setup.tex
Testing image setup

In our case, we have our configuration scripts are stored in a \texttt{.zip}
file located in a web server. We first retrieve this compressed file with
\texttt{wget} and unzip it locally into our Raspbian lite image. These
commands and the output of the last one are shown as follows:

@@

Now,

@@

Hence, we define the hostnames based on the \ac{MAC} addresses
of the \ac{Raspi}s wired Ethernet interface. Prior to this stage, the
\ac{MAC} address of a network card can be found using the command
\texttt{ifconfig} or \texttt{ip addr} on a given \ac{Raspi}.
We store the \ac{MAC} addresses and hostnames of the \ac{Raspi}s in the
configuration file \texttt{\${ROOTDIR}/home/pi/rasp\_config/nodes.csv} as
shown:

@@

The testbed administrator has to insert the \ac{MAC} addresses and hostnames
of his/her \ac{Raspi}s obtained previously in the format shown in the
configuration file. Once we have defined the hostnames in
\texttt{\${ROOTDIR}/home/pi/rasp\_config/nodes.csv}, we use the following
\ac{Bash} script to have each \ac{Raspi} assign its hostname:

@@

It is likely that the testbed administrator needs to either change or add
scripts to configure the \ac{Raspi}s. This would be tedious to distribute to
all \ac{Raspi}s at a later stage. We ease this task by making the \ac{Raspi}s fetch the
configuration scripts during start up before running the configuration scripts.

The below script attempts to download/update the scripts:

>>>>

In our case, we have our configuration scripts stored in a \texttt{.zip}
file located in a web server. We first retrieve this compressed file with
\texttt{wget} and unzip it locally into our Raspbian lite image. These
commands and the output of the last one are shown as follows:

@@

The unzippped files are one configuration file and three configuration
scripts put in the newly created \texttt{\${ROOTDIR}/home/pi/rasp\_config/}
folder in the image. In what follows, we describe which features do we
require all the \ac{Raspi}s to have and how are they achieved with
these configuration scripts.

@@

Hence, we define the hostnames based on the \ac{MAC} addresses
of the \ac{Raspi}s wired Ethernet interface. Prior to this stage, the
\ac{MAC} address of a network card can be found using the command
\texttt{ifconfig} or \texttt{ip addr} on a given \ac{Raspi}.
We store the \ac{MAC} addresses and hostnames of the \ac{Raspi}s in the
configuration file \texttt{\${ROOTDIR}/home/pi/rasp\_config/nodes.csv}. A
sample of our file is shown as follows:

@@

The testbed administrator has to insert the \ac{MAC} addresses and hostnames
of his/her \ac{Raspi}s obtained previously in the format shown in the
configuration file. Once we have defined the hostnames in
\texttt{\${ROOTDIR}/home/pi/rasp\_config/nodes.csv}, we use the
\texttt{\${ROOTDIR}/home/pi/rasp\_config/set\_hostname}
\ac{Bash} script to have each \ac{Raspi} assign its hostname:

@@

It is possible that the testbed administrator requires to add other
scripts to configure the \ac{Raspi}s besides the ones introduced here.
This would be tedious to distribute to all \ac{Raspi}s at a later stage.
We ease this task by making the \ac{Raspi}s fetch all the configuration
scripts during start up from a \texttt{.zip} file before running the
configuration scripts. The below script attempts to download/update the
scripts:
